An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-12-17 article.tex
KM edits done (except tables)

% \begin{abstract}
% \end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

@@

Historically strong demands for Australian wine have helped to create a thriving industry. However, recent pressures brought on by a loss of tourism and labour due to the COVID-19 pandemic, the global freight crisis, war in Europe, tariffs and rising inflation has negatively affected the industry's outlook \citep{wineaustraliaNationalVintageReport2021,wineaustraliaAustralianWineProduction2021}. The 2021-2022 financial year alone saw a decline of 19\% in exports solely due to tariffs \citep{wineaustraliaNationalVintageReport2022}. A greater understanding of the different underlying conditions leading to improved performance in agricultural productivity and sustainability at scale are key to making data-informed decisions to aid in increasing a nations agricultural sustainability \citep{oecdInnovationProductivitySustainability2019}. Specifically within the Australian Wine and vine industry there is a need to further understand the driving relationships between resource use and economic output, where these relationships can lead to determining better and efficient methods and develop benchmarks with local growers \citep{lukemanciniUnderstandingAustralianWine2020}.
\par
An unprecedented amount of data regarding the Australian winegrowing industry has been collected through Sustainable Winegrowing Australia, offering new insights into the driving economic forces of the Australian wine industry. This dataset allows insights into the economic outcome of vineyards through the incorporation of operating costs and grape revenue from grape sales within the data. We use this data to study these economic outcomes and their statistical relationships to vineyards' utilisation of the resources. We further compare the relationships between different resources to address the extensive collinearity found within the data \citep{chenXGBoostScalableTree2016}. We adopt XGBoosted models for this analysis because they are able to overcome multicollinearity as well as highlight the level of importance that predictor variables have on response variables.

@@

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to support grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \small
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{Number of Classes} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & KGs of Nitrogen & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
\normalsize
The data originally contained only two multiclass variables: year and region. Related binary variables, such as the use of river water and the use of dam water, were combined to create a single multiclass variable. This was done by first converting each combination that occurred into a unique category (such as river and damn water used, as opposed to the two separate categories prior). These variables were then one-hot-encoded, changing each variable class into a binary value, with one indicating the presence of the class and zero indicating its absence. Further details about classes and their frequency is available in the appendices.
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees, described in more detail below (and further in the appendix), were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. XGBoosted trees are a boosted tree ensemble method that can be used to classify classes, or predict continuous response variables. They were chosen for this analysis as the data contained a mixture of class and continuous variables. Moreover, XGBoosted trees are unaffected by multicollinearity, and offer high predictive performance for a wide variety of purposes \citep{chenXGBoostScalableTree2016}.

@@

XGBoosted models were constructed with operational cost and grape revenue as the predicted variables. The analyses were aimed at uncovering what factors influenced these variables and to what extent. As the purpose of the analysis was to identify relationships between variables and to show how they interact, an XGBoosted tree was created for each of the predictor variables as well. Trees for the predictor variables did not include operational cost or grape revenue as predictors. By creating an XGBoosted tree for each variable it meant that every variable would have a measure of its relative importance to every other variable (see Section \ref{sec:importance}). Together these models were used to measure the interrelationships of the ten most important variables in determining operational cost and grape revenue using variable importance. These measures of relative importance were used to illustrate the highly interrelated nature of variables within vineyards. The interaction between variables was depicted through the use of Sankey and Chord diagrams; with variable importance measures being used to show the strength of connection between the respective predictor variable and the response (see section \ref{sec:importance}).

@@

Due to constraints from the XGBoost library region could only be incorporated as a one-hot-encoded variable when used as a predictor. To better show what variables were related to region overall, another XGBoost tree was created with Region as the predicted value. The difference for this model was that relative variable importance would only be measured for each region specifically, as opposed to a variables overall importance in determining region. Separately profit (the difference between revenue and operational costs) and year was looked at in prior analyses (see appendix) but these results were not included due to low average loss values and model stability. 

@@

XGBoosted trees are an ensemble method that combines multiple decision trees together to create a more accurate predictive model. The gradient boosting aspect of the ensemble is the use of a loss function used to create new decision trees that add to the ensemble. Each new tree created is done so using a loss function that is optimised iteratively to improve upon prior tree's predictive power. The loss function can be any convex function, allowing gradient descent to traverse the loss space until, no improvements can be made via traversal. Because the loss function is only required to be convex, both classifiers and regressors can be used. Regularisation methods can also be incorporated to help prevent over fitting.

@@

Due to XGBoost creating a large amount of decision trees, the interpretability of these models is obfuscated by the intricate relationships within complicated ensembles. A measure of variable importance was the technique used to highlight a variables influence within the ensemble. Variable importance can be measured in multiple ways; we used the frequency of a variable appearing as a node within the ensemble as a measure of its importance. This measure was chosen as it connected a variable to the minimisation of its associated objective function. The measure of a variable's importance within this study can then be interpreted as how often a variable was the optimal choice in reducing the loss function of the ensemble. Importantly, multiclass variables being one-hot-encoded (see Section \ref{Data}) are given an importance score for each individual class; for example, each specific region will have its own importance score.

@@

The Sankey and Chord diagrams were constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Both Chord and Sankey diagrams illustrated variable importance through the size of the bands between two variables. The number at the end of a connection in a Sankey diagram indicates a variable's importance, or the number of times it appeared within the ensemble. Sankey and Chord  diagrams are presented together; with Sankey diagrams showing the connection of a variable to its ten most important predictor variables. Chord diagrams were used alongside a Sankey diagram to show the interconnectedness of the ten most prominent variables within its associated Sankey diagram. Chord diagrams formed circles, with variables being connected through their relative importance. The importance values for the Chord diagrams were taking from the models of those individual variables, with the diagram being simplified to just the ten variables in the associated Sankey diagram, for readability's sake.

@@

The predictive accuracy of each tree was assessed through a validation process. For each model the data was split into training data, which constituted 80\% of the original data. The remaining 20\% was used in testing and validation. Categorical data was stratified to conserve the same proportion of class occurrences between training, testing and validation data. For continuous variables 20\% was used as testing data and the models were validated using 10 repetitions of the sampling process (10-fold cross validation). $R^2$ scores were used to determine the best regression models during validation. $R^2$ was used instead of RMSE to allow the comparison of  models with different units to each other when considering how well each model extrapolated to further data. For binary and multiclass variables, validation was summarised through the accuracy, the proportion of true negatives and positives.
\par
The XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. This allowed us to utilise cross validated grid search functions when selecting for better performing hyperparameters. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables \citep{hanley1982meaning}. Multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
% \newline

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{revenue.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting revenue using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:revenue_sankey}
 \end{figure}

The prediction of revenue performed similarly to operating cost achieving an $R^2$ of 0.7716 (with a standard deviation of 0.1525). The value of predictors' relative importance was then calculated through the number of nodes used within the XGBoost. Values for relative importance were then used to construct Sankey and Chord diagrams to compare the contribution of each variable to predicting revenue.
\par
In order of importance, predictors of revenue were fuel use(petrol 307 and diesel 144), yield (285), size (216) and water use (199). Here, the values in the brackets indicate the relative importance of each variable (see \ref{fig:revenue_sankey}). Overall regions contributed to 234 nodes in the ensemble making them collectively the third most important variable. The chord diagram illustrates that vineyard area is also of high relative importance to other variables especially slashing. The overall importance of area to other variables is evident by its larger circumference within the chord diagram (see B in Figure \ref{fig:revenue_sankey}).
% The strong relationship of vineyard area to revenue and its predictors  but also has a high relative importance to the other predictors, The relation to area is likely to primarily be the effect of economies of scale, shown through its strong relations to other variables in figure \ref{fig:revenue_sankey}. Area harvested is likely also an indicator of other variables such as slashing passes its strongest connection presented.

@@

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Operating Costs using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:operating_costs_sankey}
 \end{figure}

Comparatively to revenue, operating cost performed better with the XGBoosted regression ensemble achieving an $R^2$ of 0.8025 (with a standard deviation of 0.1033). The relationships to operating cost through variable importance were found to be similar to that of revenue, with fuel, water, area and yield having the largest number relative importance (see figure \ref{fig:operating_costs_sankey}). A surprising difference is that the most important operational consideration for operating cost is the use of fungicide, compared to revenue where slashing is the most important (comparing Figure \ref{fig:region_sankey}). The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.
\par
Again, region played a determining factor overall, contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense.
\par
% . Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{region.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Region using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:region_sankey}
 \end{figure}

When considered overall, Region was a highly informative variable based on measures of importance for both operating cost and revenue. As noted above, Region was the third most important variable for determining revenue. The Barossa Valley region and Tasmania were the two most important regions in relation to revenue; these two regions are considered to be some of the highest revenue per hectare regions in Australia \citep{wineaustraliaNationalVintageReport2022}. These two regions are also relative opposites in winegrowing climates with the Barossa having a warm and dry climate focussing on Shiraz grapes and Tasmania having a cool wet climate that favours Pinot. 
\par
As also noted above Region was also a key determinant of operating costs. Again Tasmania was the most important, followed by the Adelaide Hills. In contrast to revenue, both climates are considered cool and wet, and warmer drier regions such as the Barossa and Hunter Valley only contributed roughly half the same number of nodes to the ensemble. Based on further analysis of Regions (Figure \ref{fig:region_sankey}) the inclusion of slashing and fungicide spraying is the likely reason with fungal and weed pressure being greater in cooler wetter regions.
\par
The XGBoost ensemble, did not perform well when predicting operating costs or revenue with 56.82\% accuracy (50.58\% validation accuracy). The difference in accuracy is in part due to the large number of classes (58 regions). The ensemble had a great emphasis on area, water, fuel and yield as determining factors (see Figure (\ref{fig:region_sankey}). 
% Although water and diesel were two of the three most frequently occurring variables in predicting region, they were not as connected to the other predictor variables as Yield and area harvested were.
\par
Many of the regions had significantly lower reporting rates, resulting in much poorer classification performance. The regions with the most samples performed the best. Bordering regions were routinely grouped together and misclassified as the same region. Two areas that suffered the most from this were the Limestone Coast (cool coastal areas in South Australia) and the warmer inland regions along the Murray Darling.

\section{Discussion}

This study explored the relationships between vineyard resource use, operations and geographical properties to revenue and operating costs. The analysis was based on a large national study of 6049 samples collected over ten years. Three main findings were identified. First, the most important predictors of revenue and operating costs were fuel, yield and area. Secondly, area and fuel were highly interrelated to other variables (see Figure \ref{fig:operating_costs_sankey} and Figure \ref{fig:revenue_sankey}). Finally, the relative importance of predictor variables for region, differed from Revenue and operating costs, with water use being more prominent than yield. Region was also more prominent than illustrated in the Sankey diagrams due to the relative importance for operating cost and revenue being calculated for individual regions and not all regions together. In its entirety region contributed third most prominently in relative importance to revenue, and was of the most relative importance in determining operating costs.

@@

Several physical parameters such as climate, geography and soil are predetermined by a vineyard's location; making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}.
The association between yield and region is demonstrated by its rank of fourth-highest variable importance when determining region (see Figure \ref{fig:region_sankey}).

@@

In part some winegrowing strategies are restricted simply through access to water resources. Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region because vineyards in regions without pressurised water will need to use more fuel to pressurise their irrigation systems.

@@

Operational costs showed similar importance across fuel, water and tractor use. The dominating factor of area likely played a large part in determining how costly a tractor pass would be, or in defining the ratio of water applied to the amount of vines. The node frequency was high for area but much lower in general across the other variables, which could indicate the need to be specific when attempting to determine the cause of a operational cost. Although it was attempted to capture the complexity between how variables interacted when determining operational costs (see Figure \ref{fig:operating_costs_sankey}), it is likely yet more complicated. An example of how interrelated operational costs can be, is 

@@

As predictions are made using additive tree functions, XGboosted trees can be used for classification or regression. The difference between a prediction, $\phi(x_i)$, and actual variable, $f_{k}(x_i)$, is a differentiable convex loss function $l$. These properties of $l$ allow the function to be versatile in which objective we choose to optimise for, which is also important in being able to process both continuous and categorical variables. To optimise $l$, the difference is calculated for the i-th instance at the t-th iteration.
\subsection{Loss functions}

>>>>

\begin{abstract}

 The Australian wine industry is a major part of Australia's agricultural sector. As global demands change and new pressures on the industry present themselves, a more sustainable approach is needed. Through a nationwide data set, collected over ten years, we link key variables in determining vineyard operational costs and revenue through the use of XGBoost. We use a measure of relative importance to show the interrelated nature of these variables and the comparative influence they have on one another. We present these connections through the use of Sankey and Chord diagrams to show the important predictors of revenue and operating costs and their strong interrelatedness. Furthermore, we connect these variables to different wine regions, highlighting the complex influence of location on the use of different resources. The study provides valuable insights into the multifaceted dynamics governing operational costs and revenue, illustrating how factors such as water and fuel use impacts on operational costs and how different seasonal events affect these operations.

\end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

@@

Historically strong demands for Australian wine have helped to create a thriving industry. However, recent pressures brought on by a loss of tourism and labour due to the COVID-19 pandemic, the global freight crisis, war in Europe, tariffs and rising inflation have negatively affected the industry's outlook \citep{wineaustraliaNationalVintageReport2021,wineaustraliaAustralianWineProduction2021}. The 2021-2022 financial year alone saw a decline of 19\% in exports solely due to tariffs \citep{wineaustraliaNationalVintageReport2022}. A greater understanding of the different underlying conditions leading to improved performance in agricultural productivity and sustainability at scale is key to making data-informed decisions increase a nation's agricultural sustainability \citep{oecdInnovationProductivitySustainability2019}. Specifically within the Australian wine and vine industry, there is a need to further understand the driving relationships between resource use and economic output, which can help to determine more cost effective and efficient methods and develop benchmarks with local growers \citep{lukemanciniUnderstandingAustralianWine2020}.
\par
An unprecedented amount of data regarding the Australian winegrowing industry has been collected through Sustainable Winegrowing Australia, offering the potential for new insights into the driving economic forces of the Australian wine industry. A major part of the potential for insight within this dataset comes from the incorporation of operating costs and grape revenue from grape sales within the data. In this paper, we use data to study economic outcomes and their statistical relationships to vineyards' utilisation of the resources. We further compare the relationships between different resources to address the extensive collinearity found within the data \citep{chenXGBoostScalableTree2016}. We adopt  a popular, relatively new machine learning method, XGBoost, for this analysis because it is able to overcome multicollinearity as well as highlight the level of importance that predictor variables have on response variables.

@@

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia (SWA), Australia's national wine industry sustainability program. SWA aims to support grape growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \small
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{Number of Classes} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & KGs of Nitrogen & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
\normalsize
The data originally contained only two multiclass variables: year and region. For this case study, related binary variables, such as the use of river water and the use of dam water, were combined to create multiclass variables such as water source. Further details about these variables, their classes and their frequency is available in the Appendix.
\par
The variable Region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

\subsection{XGBoost}
XGBoost (eXtreme Gradient Boosting), described in more detail below (and further in the Appendix), were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. XGBoost is a type of machine learning method that constructs and ensemble of decision trees to predict or estimate an output variable (the response) based on a number of input variables. The ensemble, can be used to classify classes or predict a continuous response, depending on the nature of the output variable. They were chosen for this analysis as the data contained a mixture of class and continuous variables. Moreover, XGBoost is unaffected by multicollinearity, and offer high predictive performance for a wide variety of purposes, and are capable of identifying and ranking variables and interactions in order of relative importance \citep{chenXGBoostScalableTree2016}.

@@

Four sets of analyses were conducted. In the first set, two XGBoost models were developed, with operational cost and grape revenue as the response variables. The analysis of operational cost and revenue included all variables in Table \ref{tab:vars}. The second set of analyses focused on identifying relationships between the input variables themselves, creating XGBoost models for each other variable so that every variable would have a measure of its relative importance to every other variable (see Section \ref{sec:importance}). Together these models were used to measure the interrelationships of the ten most important variables in determining operational cost and grape revenue using variable importance. These measures of relative importance were used to illustrate the highly interrelated nature of variables within vineyards. The interaction between variables was depicted through the use of Sankey and Chord diagrams; with variable importance measures being used to show the strength of connection between the respective predictor variables and the response (see section \ref{sec:importance}).

@@

The third analysis was an XGBoost tree with Region as the response variable. The difference for this model was that relative variable importance for each variable would be measured for the overall importance in determining region, as opposed to a variable's connection to each region specifically. The fourth analysis focussed on profit (the difference between revenue and operational costs) and year, however these results were not included due to low average loss values and model stability (see Appendix).

@@

XGBoost is an ensemble method that combines multiple decision trees together to create a more accurate predictive model. The gradient boosting aspect of the ensemble is the use of a loss function to create new decision trees that add to the ensemble, improving its predictive power. The loss function is optimised iteratively to improve upon prior trees. The loss function can be any convex function, allowing gradient descent to traverse the loss space until no substantive improvements can be made via traversal. Because the loss function is only required to be convex, both classifiers and regressors can be used. Regularisation methods can also be incorporated to help prevent over fitting. This makes XGBoost incredibly versatile and accurate, whilst still being interpretable compared to other machine learning methods.

@@

XGBoost creates a large number of decision trees in the ensemble, it is hard to directly interpret the model and the derived intricate relationship between the variables. Variable importance can be measured in multiple ways, in this paper we used the frequency of a variable appearing as a node within the ensemble as a measure of its importance. This measure can be interpreted as how often a variable was the optimal choice in reducing the loss function of the ensemble. Multiclass variables are given an importance score for each individual class;  for example, in the first set of analyses each specific region will have its own importance score, as will Year, Irrigation Type, etc (see Table \ref{tab:vars}).

@@

The Sankey and Chord diagrams were constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Both Chord and Sankey diagrams illustrated variable importance through the size of the bands between two variables. The number at the end of a connection in a Sankey diagram indicates a variable's importance (the number of times it appeared within the ensemble). Sankey and Chord diagrams are presented together; with Sankey diagrams showing the connection of a variable to its ten most important predictor variables and chord diagrams showing the interconnectedness of the ten most prominent variables within its associated Sankey diagram. Chord diagrams formed circles, with variables being connected through their relative importance.

@@

The predictive accuracy of each tree was assessed through a validation process. For each model, a sample of 80\% of the data was used for training the model and the remaining 20\% was used for testing and validation. Categorical data were stratified to conserve the same proportion of class occurrences between the training, testing and validation data. The models were validated using 10 repetitions of the sampling process (10-fold cross validation). $R^2$ scores were used to determine the best regression models during validation. For analyses with continuous responses $R^2$ was used instead of RMSE to allow the comparison of  models with different units to each other when considering how well each model extrapolated to further data. For binary and multiclass variables, validation was summarised through the accuracy, the proportion of true negatives and positives.
\par
As with most machine learning methods, a key component of the XGBoost model setup was the tuning of hyperparameters. The XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. This allowed us to utilise cross validated grid search functions when selecting for better performing hyperparameters. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables \citep{hanley1982meaning}. Multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

@@

The below sections present each of the analyses conducted within this study. This includes the three analyses for Revenue, Operational Cost and Region, with the fourth and final analysis on profit and yield presented in the appendix.
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
% \newline

@@

The predictive performance of the XGBoost model for revenue performed similarly to operating cost, for achieving an $R^2$ of 0.77 (with a standard deviation of 0.15). 
\par
The most important predictors of revenue were fuel use (petrol 307 and diesel 144), yield (285), size (216) and water use (199). The values attached to each variable indicate the relative importance of the variable (number of times selected in the tree ensemble, see Section \ref{fig:revenue_sankey}). Overall regions contributed to 234 nodes in the ensemble making them collectively the third most important variable. The chord diagram (see Figure \ref{fig:revenue_sankey}) illustrates that vineyard area is also of high relative importance to other variables, especially slashing. The overall importance of Area to other variables is evident by its larger circumference within the chord diagram.
% The strong relationship of vineyard area to revenue and its predictors  but also has a high relative importance to the other predictors, The relation to area is likely to primarily be the effect of economies of scale, shown through its strong relations to other variables in figure \ref{fig:revenue_sankey}. Area harvested is likely also an indicator of other variables such as slashing passes its strongest connection presented.

\begin{figure}[htb]
  \label{fig:revenue_sankey}
  \resizebox{\textwidth}{!}{
  \includegraphics{revenue.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting revenue using XGBoost as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}
 \end{figure}

@@

Compared to revenue, the predictive performance of XGBoost model for operating cost was slightly better, with an $R^2$ of 0.80 (with a standard deviation of 0.10). Similar to revenue, the most iomportant predictors of operating cost were fuel, water, area and yield (see figure \ref{fig:operating_costs_sankey}). A surprising difference was the change in relative importance of activities involving tractor passes where the use of fungicide was more important for operational costs, compared to revenue, where slashing was more important (see Figure \ref{fig:region_sankey}). The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.
\par
Again, Region played a determining factor overall, contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense.
\par
% . Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).
\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Operating Costs using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:operating_costs_sankey}
 \end{figure}

@@

Region was a highly informative variable based on measures of importance for both operating cost and revenue. As noted above, Region was the third most important variable for determining revenue. The Barossa Valley region and Tasmania were the two most important regions in relation to revenue; these two regions are considered to be some of the highest revenue per hectare regions in Australia \citep{wineaustraliaNationalVintageReport2022}. These two regions are also relative opposites in winegrowing climates with the Barossa having a warm and dry climate focussing on Shiraz grapes and Tasmania having a cool wet climate that favours Pinot. 
\par
As also noted, above Region was also a key determinant of operating costs. Again Tasmania was the most important, followed by the Adelaide Hills. In contrast, the regions of highest relative importance were warmer and drier, such as the Barossa and Hunter Valley. The higher relative importance of slashing and fungicide spraying is the likely due to fungal and weed pressure being greater in cooler wetter regions variables than in drier regions.
\par
The XGBoost ensemble for Region achieved an accuracy of 56.82\% (and 50.58\% validation accuracy). The difference in accuracy compared to the other models is in part due to the large number of classes (58 regions). The ensemble had a great emphasis on area, water, fuel and yield as determining factors (see Figure (\ref{fig:region_sankey}). 
% Although water and diesel were two of the three most frequently occurring variables in predicting region, they were not as connected to the other predictor variables as Yield and area harvested were.
\par
Substantially many of the regions had lower reporting rates, resulting in much poorer classification performance. The regions with the most samples performed the best likely due to the disparity in sample sizes. Bordering regions were routinely grouped together and misclassified as the same region. When scrutinising each class explicitly, the two areas that suffered the most from this were the Limestone Coast (cool coastal areas in South Australia) and the warmer inland regions along the Murray Darling.

\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{region.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Region using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:region_sankey}
 \end{figure}
\section{Discussion}

This study explored the relationships between vineyard resource use, operations and geographical properties to revenue and operating costs. The analysis was based on a large national study of 6049 samples collected over ten years. Three main findings were identified. First, the most important predictors of revenue and operating costs were fuel, yield and area. Secondly, area and fuel were highly interrelated to other variables (see Figure \ref{fig:operating_costs_sankey} and Figure \ref{fig:revenue_sankey}A). Finally, the relative importance of predictor variables for Region, differed from Revenue and Operating costs, with Water Use being more prominent than Yield. Region was also more prominent than illustrated in the Sankey diagrams due to the relative importance for operating cost and revenue being calculated for individual regions and not all regions together. In its entirety, was the third most important predictor of revenue and the most important predictor for operating costs, relative to the other variables consideration in the analyses.

@@

Several physical parameters such as climate, geography and soil are predetermined by a vineyard's location, making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}.
The association between yield and region is demonstrated by yield apparing as the fourth most important variable when determining region (see Figure \ref{fig:region_sankey}).

@@

In part, some winegrowing strategies are restricted simply through access to water resources. Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region because vineyards in regions without pressurised water will need to use more fuel to pressurise their irrigation systems.

@@

Operational costs showed similar importance across fuel, water and tractor use. The dominating factor of area likely played a large part in determining how costly a tractor pass would be, or in defining the ratio of water applied to the amount of vines. The relative importance was high for area but much lower in general across the other variables, which could indicate the need to be specific when attempting to determine the cause of a operational cost. Although these analyses attempted to capture the complexity between how variables interacted when determining operational costs (see Figure \ref{fig:operating_costs_sankey}), in reality these relationships are likely even more complicated. An example of how interrelated operational costs can be, is 

@@

As predictions are made using additive tree functions, XGboost can be used for classification or regression. The difference between a prediction, $\phi(x_i)$, and actual variable, $f_{k}(x_i)$, is a differentiable convex loss function $l$. These properties of $l$ allow the function to be versatile in which objective we choose to optimise for, which is also important in being able to process both continuous and categorical variables. To optimise $l$, the difference is calculated for the i-th instance at the t-th iteration.
\subsection{Loss functions}
